Manuscript draft

### 2019-07-18 manuscript/manuscript draft.Rmd
update manuscript draft

@@

The best multivariate models explained similar amounts of variation to

**Mean annual temperature.** All carbon fluxes show a linear increase with temperature.  
**Temperature seasonality and annual temperature range.** These two climate variables are strongly correlated, and so only temperature seasonality is presented in figure 4. Productivity is highest where temperature seasonality = 0, and at an annual temperature range of 15$^\circ$C or lower. GPP, NPP, ANPP, and R~root~ show a polynomial relationship with both variables, and BNPP~root~ shows a polynomial relationship with annual temperature range. As seasonality increases, these variables show a more rapid decrease in productivity. ANPP~foliage~ and ANPP~woodystem~ show a linear relationship with both variables.  
**Mean annual precipitation.** Despite being a poor predictor of productivity, the results indicate that, for the majority of fluxes, productivity increases with precipitation, up until a saturation point at between 3000 and 4000mm annual precipitation, above which productivity starts to decrease. The notable exception to this is GPP, which shows a significant (p<0.0001) linear increase with precipitation up to measures of nearly 6000mm annually, although the explanatory power of this model was low (R-squared = 0.15).
**Potential evapotranspiration.** All fluxes, with the exception of BNPP~rootfine~ and R~root~ show a strong increase with potential evapotranspiration at values below 1000mm. Between 1200 and 1700mm productivity peaks, and begins to decrease at values above 1800mm.

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivariate_models <- read.csv("C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/multivariate_models.csv", stringsAsFactors = FALSE, check.names = FALSE)
rownames(multivariate_models) <- c("GPP", "NPP", "ANPP", "ANPP\\textsubscript{foliage}", "ANPP\\textsubscript{woody stem}", "BNPP", "BNPP\\textsubscript{root}", "R\\textsubscript{root}")
kable(multivariate_models, format = "latex", booktabs = TRUE, caption = "Multivariate model output summary. For each carbon flux, correlation coefficients are presented for the two climate variables which explain the most variation when included in a multivariate model. If the model includes an interactive effect, correlation coefficients for the interaction are presented. Results for R\\textsubscript{auto} are not presented here due to the small sample size (n = 14).  ", escape = FALSE, row.names = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1:10, width = "2cm") %>%
  add_header_above(c(" ", " ", " ", "Correlation coefficients of climate variables" = 6, " "))

@@

| Variable | Latitude | Mean annual temperature | Temperature seasonality | Potential evapotranspiration |
|----------|----------|----------|----------|----------|
| R~auto~ | 0.64 | 0.83 | 0.54 | 0.63 |
| GPP | 0.66 | 0.61 | 0.75 | 0.40 |
| NPP | 0.51 | 0.49 | 0.52 | 0.34 |
| ANPP | 0.50 | 0.45 | 0.47 | 0.32 |
| ANPP~foliage~ | 0.55 | 0.63 | 0.54 | 0.40 |
| ANPP~woodystem~ | 0.25 | 0.23 | 0.20 | 0.26 |
| BNPP~root~ | 0.31 | 0.26 | 0.31 | 0.32 |
| BNPP~rootfine~ | 0.14 | 0.11 | 0.16 | 0.11 |
| R~root~ | 0.25 | 0.21 | 0.29 | 0.04* |

Table: R-squared values presented for four climate variables. Values marked * are not significant.

@@

>>>>

```{r results="asis", include=FALSE}
cat("
<style>
caption {
      font-size: 0.75em;
    }
</style>
")
```

@@

Including a second climate term in the models didn't tend to significantly increase the explanatory power of the models. The best multivariate models for each carbon flux have r-squared values in the range of those recorded for models with a single climate term. However, the multivariate models do capture the additive and interactive effects of temperature and water availability.

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivariate_models <- read.csv("C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/multivariate_models.csv", stringsAsFactors = FALSE, check.names = FALSE)
rownames(multivariate_models) <- c("GPP", "NPP", "ANPP", "ANPP\\textsubscript{foliage}", "ANPP\\textsubscript{woody stem}", "BNPP", "BNPP\\textsubscript{fine root}", "R\\textsubscript{root}")
kable(multivariate_models, format = "latex", booktabs = TRUE, caption = "Multivariate model output summary. For each carbon flux, correlation coefficients are presented for the two climate variables which explain the most variation when included in a multivariate model. If the model includes an interactive effect, correlation coefficients for the interaction are presented. Results for R\\textsubscript{auto} are not presented here due to the small sample size (n = 14).  ", escape = FALSE, row.names = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1:10, width = "2cm") %>%
  add_header_above(c(" ", " ", " ", "Correlation coefficients of climate variables" = 6, " "))

@@

| Variable | Latitude | Mean annual temperature | Temperature seasonality | Potential evapotranspiration | Multivariate model |
|----------|----------|----------|----------|----------|----------|
| R~auto~ | 0.64 | 0.83 | 0.54 | 0.63 | NA |
| GPP | 0.66 | 0.61 | 0.75 | 0.40 | 0.74 |
| NPP | 0.51 | 0.49 | 0.52 | 0.34 | 0.56 |
| ANPP | 0.50 | 0.45 | 0.47 | 0.32 | 0.49 |
| ANPP~foliage~ | 0.55 | 0.63 | 0.54 | 0.40 | 0.66 |
| ANPP~woodystem~ | 0.25 | 0.23 | 0.20 | 0.26 | 0.26 |
| BNPP~root~ | 0.31 | 0.26 | 0.31 | 0.32 | 0.36 |
| BNPP~rootfine~ | 0.14 | 0.11 | 0.16 | 0.11 | 0.19 |
| R~root~ | 0.25 | 0.21 | 0.29 | 0.04* | 0.47 |

Table: R-squared values presented for latitude, three climate variables, and the best multivariate model for each carbon flux. Values marked * are not significant.

@@

This pattern is also seen in the r-squared values for multivariate models.
